---
output: 
  html_document: 
    fig_caption: yes
    keep_md: yes
---
This is Reproducible Research Project 1
==========================================

For step 1: getting and processing data

```{r step1,echo=TRUE}
library(dplyr)
mydata <- read.csv("activity.csv", sep = ",")
mydata <- tbl_df(mydata)
```

Step 2: Histogram of the total number of steps taken each day

```{r step2, echo=TRUE}
totalsteps <- tapply(mydata$steps, mydata$date, sum)
hist(totalsteps, main = "Total number of steps taken each day", col = "red")
dev.copy(png, file = "Step 2.png")
dev.off()
```

Step 3: Mean and median number of steps taken each day
mean
```{r mean, echo=TRUE}
tapply(mydata$steps, mydata$date, mean)
```
medain
```{r median, echo=TRUE}
tapply(mydata$steps, mydata$date, median)
```

Step 4: Time series plot of the average number of steps taken
```{r step,echo=TRUE}
avsteps <-tapply(mydata$steps, mydata$interval, mean, na.rm = TRUE)
mydata <- transform(mydata, interval = as.factor(interval))
plot(levels(mydata$interval),avsteps, type = "l", main = "Average number of steps",xlab = "5-minute interval", ylab = "Average of steps in all days")
dev.copy(png, file = "Step 4.png")
dev.off()
```

step 5: The 5-minute interval that, on average, contains the maximum number of steps
```{r step5,echo=TRUE}
x <- mydata[max(na.omit(mydata$steps)),"interval"]
as.numeric(as.character(x))
```

step 6: Code to describe and show a strategy for imputing missing data
Number of missing values
```{r step6, echo=TRUE}
s <- mydata$steps
length(s) - length(na.omit(s))
```
Filling in all of the missing values with mean values
```{r echo=TRUE}
mydata <- transform(mydata, date= as.character(date))
nas <- which(is.na(mydata$steps))
df <- na.omit(mydata)
step <- tapply(df$steps, df$date, sum)
mean <- mean(step)
newdata <- mydata
newdata$steps[nas] <- mean
```

Step 7: Histogram of the total number of steps taken each day after missing values are imputed
```{r step7, echo=TRUE}
newsteps <- tapply(newdata$steps, newdata$date, sum)
newsteps <- as.numeric(newsteps)
hist(newsteps, main = "Total number of steps taken each day after missing values are imputed", col = "red")
```

mean total number of steps taken per day
```{r echo=TRUE}
as.integer(tapply(newdata$steps, newdata$date, mean))
```

medain total number of steps taken per day
```{r echo=TRUE}
as.integer(tapply(newdata$steps, newdata$date, median))
```

Step 8: Panel plot comparing the average number of steps taken per 5-minute interval across weekdays and weekends
```{r step8,echo=TRUE}
days <- newdata$date
days <- as.character(days)
days <- as.Date(days)
days <- weekdays(days)
Sys.setlocale("LC_ALL", "English")
for(i in 1:length(days)){
     if (days[i]=="Saturday") {days[i] <- "weekend"}
     else {(days[i] <- "weekday")}
}
newdata <- mutate(newdata, days)
newdata <- transform(newdata, days=as.factor(days))
wend <- filter(newdata, days=="weekend")
wday <- filter(newdata, days=="weekday")
wendm <- tapply(wend$steps, wend$interval, mean)
wdaym <- tapply(wday$steps, wday$interval, mean)
```

```{r plot,fig.height=4,fig.width=8,fig.show="hold",fig.align="center",fig.path="fig/",tidy=TRUE,eval=TRUE}
par(mfrow=c(1,2))
plot(levels(mydata$interval), wendm, ylim = c(1350,1600), type = "l", xlab = "Interval",ylab = "steps", main = "Weekend")
plot(levels(mydata$interval), wdaym, ylim = c(1350,1600), type = "l", xlab = "Interval",ylab = "steps", main = "Weekday")
```